Assessing Material Inventory Uncertainties in Integrated Fuel Cycle Simulations

### 2018-07-20 paper.tex
english

This preliminary study may suggest that the most important contributions to
natural uranium consumption and fissile inventory come from the parameters that
govern the exchange of material between facilities, and not from the physical
parameters that describe those facilities, such as thermal power or fuel
enrichment. Moreover such conclusions might change in a different scenario with
different hypothesis: not considering radioactive decay remove the decay of
$^{241}$Pu during cooling and considering a transition to fast reactors reduce
the effect of composition change induced by the cycle length variations.

@@

This study aims to be a proof-of-principle for uncertainty propagation in
potential commercial fuel cycle transition.  While it has demonstrated the
capability to measure the uncertainty on output fuel cycle metrics and their
relative contributions, it has only been applied to systematic uncertainties per
facilities.  This kind of study will to be extended to random uncertainty (new
parameter values as a function of time) and completely systematic uncertainty
(shared by all the facilities of a kind). Additionally more sophisticated
methods needs to be used to assess precisely each parameter contributions..

>>>>

This preliminary study may suggest that the most important contributions to
natural uranium consumption and fissile inventory come from the parameters that
govern the exchange of material between facilities, and not from the physical
parameters that describe those facilities, such as thermal power or fuel
enrichment. Moreover such conclusions might change for different scenarios with
different hypothesis: not considering radioactive decay remove the decay of
$^{241}$Pu during cooling and considering a transition to fast reactors reduce
the effect of composition change induced by the cycle length variations.

@@

This study aims to be a proof-of-principle for uncertainty propagation in
potential commercial fuel cycle transition.  While it has demonstrated the
capability to measure the uncertainty on output fuel cycle metrics and their
relative contributions, it has only been applied to systematic uncertainties per
facilities.  This kind of study will be extended to random uncertainty (new
parameter values as a function of time) and completely systematic uncertainty
(shared by all the facilities of a kind). Additionally more sophisticated
methods needs to be used to assess precisely each parameter contributions..
